Review of Group 8 by Group 1

### 2015-02-13 rmtw/a3/latex8.tex
All but Purpose Completed

\SubSection{Existing Literature}
Use parts of the CM report. 
Most relevant is probably Jani's but could find stuff in the other's too.

According to literature, changes in companies are commonly implemented following either Software Process Improvement (SPI) or change management (CM) strategies [CITE BOTH].

SPI is X and is usually performed with XYZ

@@

Literature tells us that there are many factors for both success and failure when implementing change. X define this type of activity as Software Process Improvement (SPI) [GET REF]. SPI utilises many methods and techniques to implement changes in a companies existing software process.

CMMI is such an example of one of these methods.

@@

\SubSection{Motivation for Research}
Performing this study would therefore be an attempt at filling in a gap in literature. Academia would be interested in this for its own merit or, most likely, as a stepping stone to further research.

Industry are just as likely to be interested. We have performed this study at an organisation, to which the results would be of great value. The organisation in question has had problems in the past with implementing effective change to keep up with their competition.

>>>>

\SubSection{Existing Literature}
According to literature, changes in companies are commonly implemented following either Software Process Improvement (SPI)\cite{pettersson2008practitioner}\cite{unterkalmsteiner2012evaluation} or change management (CM) strategies. SPI is an attempt to alter an existing company or organisations software process, the main intention of which is to increase product quality, time to market all the while reducing inefficiency and other obstacles for creating good software.

@@

CM on the other hand could be seen as an umbrella for many theories and strategies. Such an example of this is the concept of innovation values fit by [CITE].

@@

\SubSection{Motivation for Research}
Performing this study would therefore be an attempt at filling in a gap in literature. Academia would be interested in this for its own merit or, most likely, as a stepping stone towards further research.

Industry is just as likely to be interested as change is something they face regularly. If this study can help to shed some light about specific methods of to help accommodate change. The study will be conducted in tandem with an organisation, to which the results would also be of great value. The organisation in question has had problems in the past with implementing effective change to keep up with their competition.
